### 2022-12-14 README.Rmd
Updates

# `simbased`: Simulation-Based Inference for Regression Models

@@

`simbased` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.

@@

You can install the development version of `simbased` from [GitHub](https://github.com/) with:

@@

The `simbased` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

`simbased` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing. We can compute the log marginal risk ratio below:

@@

We can also use `simbased` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:

@@

`simbased` offers parallel processing for all estimation functions to speed up computation.

>>>>

# `{simbased}`: Simulation-Based Inference for Regression Models

@@

`{simbased}` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.

@@

You can install the development version of `{simbased}` from [GitHub](https://github.com/) with:

@@

The `{simbased}` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `{simbased}` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

`{simbased}` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing. We can compute the log marginal risk ratio below:

@@

We can also use `{simbased}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:

@@

`{simbased}` offers parallel processing for all estimation functions to speed up computation.
